---
title: "13_1_do_absences_affect_your_grade"
format: html
---

Before anything else, load the libraries by running the code block below.

```{r}
library(tidyverse)
```

And read the data by running the code block below.

```{r}
population = read_csv("do_absences_affect_your_grade.csv")
population
```

# Step 1: Visualize the population

Then plot the data by running the code block below.

```{r}
# Start with your data
population |> 
  # Make a blank canvas for your plot
  ggplot() +
  # Decide on your x and y axes
  aes(x = days_absent, y = final_grade) +
  # Add a regression line with the "linear model" method and no error bars
  geom_smooth(method = "lm", se = FALSE) +
  # Make a scatterplot
  geom_point()
```

## Exercise 1: Describe the relationship

Remember to comment on each of these
* Direction ("positive" or "negative"
* Unusual features (e.g. gaps in the x- or y- axis, or points far from the line)
* Form (Does it look linear or nonliner?)
* Strength ("strong"? "weak"? "no relationship"?)

# Step 2: Run a Linear Regression for the population

Run the code block below to run a linear regression (AKA find the line of best fit). The results of the linear regression are in the "Coefficients" section of the output. The "(Intercept)" coefficient is the y-intercept. The "days_absent" coefficient is the slope.

```{r}
m = lm(final_grade ~ days_absent, data = population)
m
```

## Exercise 2:

What is the equation of the linear regression line? Remember to define your variables in context.

## Exercise 3:

What is the y-intercept? Is this a statistic or a parameter? Explain.

## Exercise 4:

What is the slope? Is this a statistic or a parameter? Explain.

## Exercise 5:

Interpret the slope (remember your units!).

# Step 3: Randomly sample 10 students

Sample 10 students at random from the full dataset by running the code block below.

```{r}
sample_of_10 = population |> 
  sample_n(10)
sample_of_10
```

# Step 4: Visualize your sample

Copy the code from "Step 1: Visualize the population" into the code block below.
Replace the population dataset `population` with your randomly sampled `sample_of_10`.

```{r}

```

# Step 5: Run a Linear Regression for your sample.

```{r}

```

## Exercise 6: Draw the scatterplot for your sample

## Exercise 7: What is the equation of the regression line?

## Exercise 8: What is the y-intercept? Is this a statistic or parameter? Explain.

## Exercise 9: What is the slope? Is this a statistic or parameter? Explain.

# Step 6: Collect 30 different sample slopes

```{r}
sample_10_students = function(i) {
  # Copy your code from "Step 3: Randomly sample 10 students" here
  
  # Copy your code from "Step 5: Run a linear regression for your sample" here
  
  # Do not change this code:
  m$coefficients["days_absent"]
}
sample_slopes = map_dbl(1:30, sample_10_students)
ggplot(NULL, aes(x = sample_slopes)) +
  geom_dotplot() +
  lims(x = c(-4, 4))
```

# Step 7: Inspect the full linear regression output for a sample

Randomly sample 10 students again:

```{r}
# Copy your code from "Step 3: Randomly sample 10 students" here


```

Run the linear regression for that sample:

```{r}
# Copy your code from "Step 5: Run a linear regression for your sample" here


```

So far, we've just gotten a single estimate for the y-intercept and a single estimate for the slope.
But we can do inference about the population from the sample, using the full regression output.
Run the code below to see the full regression output:

```{r}
m |> summary()
```



